Arrows for Parallel Computation

### 2018-01-06 paper/content/relwork.tex
sorting out references

The |farm| skeleton \citep{Hey1990185,Eden:PPDP01,Kuchen05} is statically task-balanced parallel |map|. When tasks' durations cannot be foreseen, a dynamic load balancing (|workpool|) brings a lot of improvement \citep{Rudolph:1991:SLB:113379.113401,Eden:PPL03,Hippold2006,PADL08HMWS,Marlow2009}. For special tasks |workpool| skeletons can be extended with dynamic task creation \cite{WPEuropar06,Dinan:2009:SWS:1654059.1654113,brown2010ever}. Efficient load-balancing schemes for |workpool|s are subject of research \cite{Acar:2000:DLW:341800.341801,Blumofe:1999:SMC:324133.324234,vanNieuwpoort:2001:ELB:568014.379563,Chase:2005:DCW:1073970.1073974,4625841,Michael:2009:IWS:1594835.1504186}.
%
The |fold| (or |reduce|) skeleton was implemented in various skeleton libraries \cite{Kuchen2002,BUONO20102095,Dastgeer:2011:ASM:1984693.1984697,5361825}, as also its inverse, |scan|, \cite{Bischof2002,harris2007parallel}.
%
Google |map|--|reduce| is more special than just a composition of the two skeletons \cite{LAMMEL20081,Berthold2009-mr}.

>>>>

The |farm| skeleton \citep{Hey1990185,Eden:PPDP01,Kuchen05} is statically task-balanced parallel |map|. When tasks' durations cannot be foreseen, a dynamic load balancing (|workpool|) brings a lot of improvement \citep{Rudolph:1991:SLB:113379.113401,doi:10.1142/S0129626403001380,Hippold2006,PADL08HMWS,Marlow2009}. For special tasks |workpool| skeletons can be extended with dynamic task creation \cite{WPEuropar06,Dinan:2009:SWS:1654059.1654113,brown2010ever}. Efficient load-balancing schemes for |workpool|s are subject of research \cite{Acar:2000:DLW:341800.341801,Blumofe:1999:SMC:324133.324234,vanNieuwpoort:2001:ELB:568014.379563,Chase:2005:DCW:1073970.1073974,4625841,Michael:2009:IWS:1594835.1504186}.
%
The |fold| (or |reduce|) skeleton was implemented in various skeleton libraries \cite{Kuchen2002,BUONO20102095,Dastgeer:2011:ASM:1984693.1984697,5361825}, as also its inverse, |scan|, \cite{Bischof2002,harris2007parallel}.
%
Google |map|--|reduce| is more special than just a composition of the two skeletons \cite{LAMMEL20081,Berthold2009-mr}.
